\newcommand{\ntypecalalt}{Altmetric score = 4; 161 user saves, 3 social-media posts, 0 news outlets, and 1 English Wikipedia pages.}
\newcommand{\pdlimalt}{No Altmetric data to report.}
\newcommand{\warsialt}{No Altmetric data to report.}
\newcommand{\anglinalt}{No Altmetric data to report.}
\newcommand{\psychotropicalt}{No Altmetric data to report.}
\newcommand{\psychopharmalt}{Altmetric score = 3; 58 user saves, 1 social-media posts, 0 news outlets, and 1 English Wikipedia pages.}
\newcommand{\ethanolalt}{Altmetric score = 1; 60 user saves, 4 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\pathologicalalt}{Altmetric score = 94; 50 user saves, 41 social-media posts, 11 news outlets, and 0 English Wikipedia pages.}
\newcommand{\punctatealt}{Altmetric score = 5; 14 user saves, 9 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\rtwostaralt}{Altmetric score = 9; 29 user saves, 15 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\perinatalalt}{Altmetric score = 3; 17 user saves, 5 social-media posts, 0 new outlets, and 0 English Wikipedia pages.}
\newcommand{\campbellfractalalt}{Altmetric score = 1; 22 user saves, 1 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\campbellreviewalt}{Altmetric score = 2; 23 user saves, 3 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\bartelalt}{Altmetric score = 8; 13 user saves, 9 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\fothergillalt}{Altmetric score = 26; 6 user saves, 50 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\scialt}{Altmetric score = 5; 5 user saves, 7 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\dcdchangesalt}{Altmetric score = 1; 15 user saves, 1 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\dcdcontrolsalt}{No Altmetric data to report.}
\newcommand{\ironalt}{Altmetric score = 1; 34 user saves, 1 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\sickkidsalt}{Altmetric score = 1. 3 user saves, 1 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\dhcpalt}{Altmetric score = 3; 4 user saves, 6 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\carmichaelalt}{Altmetric score = 1; 3 user saves, 2 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\zhucmroalt}{Altmetric score = 10; 5 user saves, 5 social-media posts ($+ 1$ podcast), 0 news outlets, and 0 English Wikipedia pages.}

\newcommand{\scipreprintalt}{Altmetric score = 2. 0 user saves, 3 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\dhcppreprintalt}{Altmetric score = 2. 0 user saves, 5 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\mrishinyalt}{No Altmetric data to report.}
\newcommand{\sochanpreprintalt}{Altmetric score = 6. 0 user saves, 12 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\myelinchapteralt}{Altmetric score = 8; 48 user saves, 8 social-media posts, 0 news outlets, and 0 English Wikipedia pages.}
\newcommand{\oacount}{19}
